\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-03 NAR_DRAFT.tex
new papers and citations

The \batcave algorithm focuses on the tri-nucleotide context and substitution type, which has been shown to have a large effect on site-specific mutation rates \cite{Martincorena2015,Hollstein2017}.
There are, however, many other types of \textit{genomic context} which can effect local mutation rates such as replication timing, expression level, and histone occupancy \cite{Buisson2019} .
These could be very useful in computing a local or regional mutation rate, as opposed to the genome-wide but tumor-specific mutation rate used by \batcave.

>>>>

The \batcave algorithm focuses on the tri-nucleotide context and substitution type, which has been shown to have a large effect on site-specific mutation rates \cite{Martincorena2015,Hollstein2017}.
There are, however, many other types of \textit{genomic context} which can effect local mutation rates including replication timing, expression level, and chromosome organization \cite{Buisson2019,Schuster-Bockler2012,Pleasance2010} .
These could be very useful in computing a local or regional mutation rate, as opposed to the genome-wide but tumor-specific mutation rate used by \batcave.
